---
title: "Hypercube Estimator"
author: "Chi Po Choi, Amy T. Kim"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

We are developing the R package: HyperCube ([1] introduced by Rudolf Beran) which let users find Hypercube estimators much easily. Hypercube estimator is a richer class of regularized estimators of $\eta = \text{E}(y) = X\beta$, which equivalents to penalized least squares estimators with quadratic penalites and to submodel least squares estimators. Also, it minimizes the asymptotice risk under the general linear model. We explain main functions with the fundermantal theories.\cite{beran2014hypercube} Also, we demonstrate the examples in the paper and have the same results.



## Vignette Info

```{r, fig.width=7, fig.height=5}
library(HyperCube)
canadian.earnings$age <- factor(canadian.earnings$age)
plot(as.numeric(as.character(canadian.earnings$age)), canadian.earnings$log.income,
     xlab = "age", ylab = "log(income)")

D <- diffMatrix(length(unique(canadian.earnings[,1])), 5)
lambda <- c(0, 10^c(2,5,8,11))
lcolor <- 1:5

for(k in 1:5) {
  W <- lambda[k] * t(D) %*% D
  V <- plsW2V(W)
  hcmod <- hypercube( log.income ~ age -1, data=canadian.earnings, V)
  lines(as.numeric(levels(canadian.earnings$age)), hcmod$coefficients, col = lcolor[k])
}
```


```{r}
hcmodopt <- hypercubeOptimization( weight ~ mother:infant -1, data = litter)
hcmodopt$projcoef
summary(hcmodopt$est)
```

